Make manuscript figures

### 2021-10-28 scripts/R/make_manuscript_figures.rmd
fiddle with OU parameters for model figure

# Generate tree
set.seed(10)
tree <- ape::rtree(n = 3)
node_times <- POUMM::nodeTimes(tree)
edge_colors = RColorBrewer::brewer.pal(n = 4, name = diverging_palette)

# Define OU process
scale_factor <- 1000
v0 <- 3.98
theta <- 4.38
alpha <- 30.15 / scale_factor
sigma <- 3.56 / sqrt(scale_factor)

>>>>

# Generate tree
set.seed(10)
tree <- ape::rtree(n = 3)
tree$edge.length <- tree$edge.length * 6
node_times <- POUMM::nodeTimes(tree)
edge_colors = RColorBrewer::brewer.pal(n = 4, name = diverging_palette)

# Define OU process
scale_factor <- 40  # 1000
v0 <- 3.5
theta <- 4.5
alpha <- 50 / scale_factor
sigma <- 3 / sqrt(scale_factor)
